Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/pilot.tex

Figure~\ref{fig:pilot_sims} shows the average number of ballots sampled for each value of $p$ in the simulations. The vertical line denotes the stopping probability of the first round size chosen in the pilot of $140$ ballots. The average number of ballots for such a high stopping probability round schedule is high. blah blah based on plot and some numbers illustrating that point... Of course, average number of ballots is not the only metric that matters when planning an audit. For this pilot audit, extensive planning of the round schedule was not necessary because the margin was high enough the relatively few ballots were needed even to achieve the high probability of stopping. In Section~\ref{sec:workload} we consider a larger, state-wide contest where selecting the round schedule has more significant implications. Some of the ideas introduced in Section~\ref{sec:workload} we do apply to this pilot case as well.

@@

>>>>

Figure~\ref{fig:pilot_sims} shows the average number of ballots sampled for each value of $p$ in the simulations. The vertical line denotes the stopping probability of the first round size chosen in the pilot of $140$ ballots. The average number of ballots for such a high stopping probability round schedule is high. blah blah based on plot and some numbers illustrating that point... Of course, average number of ballots is not the only metric that matters when planning an audit.

@@

For this pilot audit, extensive planning of the round schedule was not necessary because the margin was high enough the relatively few ballots were needed even to achieve the high probability of stopping. In Section~\ref{sec:workload} we consider a larger, state-wide contest in Virginia where selecting the round schedule has more significant implications. Virginia also currently uses ballot polling RLAs whereas Rhode Island primarily uses batch comparison RLAs. Some of the ideas introduced in Section~\ref{sec:workload} we do apply to this pilot case as well.

### 2022-10-11 providence/sections/sims.tex

% simulations
We use simulations to provide additional evidence for theoretical claims and gain insight into audit behavior. As in \cite{simulations}, we use margins from the 2020 US Presidential election---state-wide pairwise margins between the leading two candidates of 5\% or more. Narrower margins are computationally expensive, especially for the simulations with an underyling tie, which, by design, have a low probability of stopping and hence require all rounds and quickly increase in sample size. We use the simulator in the R2B2 software library\cite{r2b2}. For each margin, for each hypothesis, we perform $10^4$ trials. RISK LIMIT. NUMBER OF ROUNDS. STOPPING PROB.

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_risk.png}
\caption{The fraction of simulated \Providence audits on tied elections that stopped in any rounds (we performed five rounds AT WHAT STOPPING PROB? RISK LIMIT?). This value is an estimate of the maximum risk of the \Providence audit.}
\label{fig:prov-risk}
\end{figure}

>>>>

% simulations
We use simulations to provide additional evidence for theoretical claims and gain insight into audit behavior. As in \cite{simulations}, we use margins from the 2020 US Presidential election---state-wide pairwise margins between the leading two candidates of 5\% or more. Narrower margins are computationally expensive, especially for the simulations with an underyling tie, which, by design, have a low probability of stopping and hence require all rounds and quickly increase in sample size. We use the simulator in the R2B2 software library\cite{r2b2}. For each margin, for each hypothesis, we perform $10^4$ trials. All trials use a $10\%$ risk limit, a maximum of $5$ rounds, and a conditional stopping probability of $0.90$ in each round. That is, each subsequent round size is selected to be large enough, assuming the announced tally is correct and given the tally of previous rounds, to give a $0.90$ probability of stopping in the current round.

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_risk.png}
\caption{The fraction of simulated \Providence audits on tied elections that stopped in any rounds (we performed five rounds at a $10\%$ risk limit). This value is an estimate of the maximum risk of the \Providence audit.}
\label{fig:prov-risk}
\end{figure}
